\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

% Font options
\usepackage[sfdefault]{roboto}  % Sans-serif font

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{\Large\bfseries\scshape\raggedright}{}{0em}{}[\titlerule]


% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeSubheading}[4]{
\vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{#3} & \textit{#4} \\
  \end{tabular*}\vspace{-7pt}
}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingList}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

\begin{center}
  \textbf{\Huge Gur Raunaq Singh} \\
  \small +91-9015154091 $|$ \href{mailto:raunaq.soni@gmail.com}{raunaq.soni@gmail.com} $|$
  \href{https://www.linkedin.com/in/gurraunaqsingh/}{linkedin.com/in/gurraunaqsingh} $|$
  \href{https://github.com/raunaqness}{github.com/raunaqness} $|$ Bangalore, India
\end{center}

\section*{Summary}
Senior AI and ML Systems Architect with 8+ years of experience designing secure, scalable AI platforms in enterprise environments processing high-volume transactional data. Specialized in distributed ML systems, Kubernetes-native orchestration, multi-cloud architectures, and Generative AI (LLMs, RAG, agentic workflows). Strong focus on MLOps, IAM-based access control, auditability, and operational resilience. Experience deploying and managing containerized workflow automation systems (n8n) on cloud infrastructure with secure API and LLM integrations.

\section{Technical Skills}
\resumeSubHeadingList
  \resumeItem{\textbf{AI/ML}: LLMs, RAG, LangChain, LangGraph, Model Monitoring}
  \resumeItem{\textbf{Cloud \& Infra}: Azure (AKS, App Services), AWS, Kubernetes, Docker, Terraform}
  \resumeItem{\textbf{Data \& Backend}: Python, SQL, Kafka, Redis, PostgreSQL, FastAPI, Django}
  \resumeItem{\textbf{MLOps}: CI/CD, MLflow, IAM, Audit Logging, Encryption, SLA Monitoring}
  \resumeItem{\textbf{Automation}: n8n (workflow automation), API integrations, Webhooks}
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingList
  \resumeSubheading
      {Aptos India}{Jan 2023 -- Present}
      {Machine Learning Engineer}{Bangalore, India}
      \resumeSubHeadingList
          \resumeItem{\textbf{Project: Aptos One} -- Enterprise Unified Commerce Platform serving 100+ global retailers and processing billions of transactions annually.}
          \begin{itemize}[leftmargin=1.4em,label=•]
              \item \small{Architected a Kubernetes-native ML orchestration control plane enabling workload-aware scheduling, checkpoint-based recovery, and distributed job lifecycle management in SLA-bound production environments.}
              \item \small{Designed secure, fault-tolerant data pipelines on GCP (BigQuery + event-driven workflows), implementing IAM-based access controls, encryption practices, and audit logging while improving processing SLAs by 35\%.}
              \item \small{Optimized cloud infrastructure and query execution strategies, reducing compute costs by 60\% (about USD 240K annual savings) while modernizing legacy systems into scalable, observable cloud-native components.}
              \item \small{Technologies: Python, GCP, Vertex AI, BigQuery, Kubernetes, Docker, Terraform, Redis, CI/CD, IAM}
          \end{itemize}
          \resumeItem{\textbf{Project: Generative AI \& LLM Support Assistant}}
          \begin{itemize}[leftmargin=1.4em,label=•]
              \item \small{Designed an enterprise-grade RAG architecture integrating structured analytics metadata and internal knowledge bases to deliver context-aware responses with improved semantic accuracy.}
              \item \small{Implemented prompt versioning, evaluation workflows, and monitoring mechanisms to reduce hallucinations by 35\% while improving traceability and observability of model outputs.}
              \item \small{Deployed containerized inference workflows using MLOps practices, enabling controlled experimentation, scalable inference, and secure knowledge isolation via vector database access controls.}
              \item \small{Technologies: Python, LangChain, LangGraph, Vertex AI, VectorDB, FastAPI, Docker, MLOps}
          \end{itemize}
      \resumeSubHeadingListEnd

  \resumeSubheading
      {Turing.com}{Apr 2022 -- Dec 2022}
      {Senior Software Engineer}{India (Remote)}
      \resumeSubHeadingList
          \resumeItem{\textbf{Project: End-to-End ML Deployment Platform}}
          \begin{itemize}[leftmargin=1.4em,label=•]
              \item \small{Designed and implemented production-grade ML pipelines using Airflow for ingestion, training, validation, and automated deployment.}
              \item \small{Standardized CI/CD and model versioning practices, reducing deployment time by 60\% and improving controlled production rollouts.}
              \item \small{Integrated monitoring and validation checks to enhance production reliability and maintainability of deployed ML systems.}
              \item \small{Technologies: Python, Django, Airflow, GCP, Docker, MLOps}
          \end{itemize}
      \resumeSubHeadingListEnd

  \resumeSubheading
      {Clickpost Pvt. Ltd.}{Apr 2021 -- Apr 2022}
      {Senior Software Engineer}{Bangalore, India}
      \resumeSubHeadingList
          \resumeItem{\textbf{Project: Cash Reconciliation Automation Platform} -- serving 1,000+ enterprise customers handling high-volume CoD transactions.}
          \begin{itemize}[leftmargin=1.4em,label=•]
              \item \small{Designed and built a high-accuracy financial reconciliation system processing large-scale transactional datasets with strict data integrity and traceability requirements.}
              \item \small{Reduced reconciliation cycle time by 95\% (from about 2 days to minutes) through parallelized processing and automated validation workflows, improving operational efficiency and financial visibility.}
              \item \small{Architected secure ingestion pipelines and scalable backend APIs under high-availability constraints, ensuring auditability and controlled access to financial data.}
              \item \small{Technologies: Python, Django, PostgreSQL, AWS, Redshift, Kafka, Docker, Kubernetes}
          \end{itemize}
      \resumeSubHeadingListEnd

  \resumeSubheading
      {Veda Labs Pvt. Ltd.}{Jul 2018 -- Apr 2021}
      {Software Engineer}{New Delhi, India}
      \resumeSubHeadingList
          \resumeItem{\textbf{Project: Video Analytics Platform} -- Computer vision platform deployed on-premise for retail analytics using CCTV footage.}
          \begin{itemize}[leftmargin=1.4em,label=•]
              \item \small{Developed containerized video analytics pipelines for edge devices.}
              \item \small{Built a Kafka-based streaming architecture for scalable, real-time processing.}
              \item \small{Technologies: Python, OpenCV, Computer Vision, Kafka, Docker}
          \end{itemize}
      \resumeSubHeadingListEnd
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingList
  \resumeItem{\textbf{Stateful AI Travel Agent (LangGraph)}}
  \begin{itemize}[leftmargin=1.4em,label=•,topsep=0pt,partopsep=0pt,parsep=0pt]
      \item \small{Engineered a graph-orchestrated, memory-aware multi-agent system for dynamic travel planning.}
      \item \small{Github: \href{https://github.com/raunaqness/ai-travel-agent}{https://github.com/raunaqness/ai-travel-agent}}
      \item \small{Demo: \href{https://ai-travel-agent.fly.dev/}{https://ai-travel-agent.fly.dev/}}
  \end{itemize}
  \resumeItem{\textbf{Workflow Automation Platform (n8n + Azure)}}
  \begin{itemize}[leftmargin=1.4em,label=•,topsep=0pt,partopsep=0pt,parsep=0pt]
      \item \small{Designed and deployed containerized n8n workflows on Azure integrating APIs and LLM services for secure, scalable process automation.}
  \end{itemize}
\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingList
  \resumeSubheading
      {Indraprastha University}{Aug 2014 -- Jun 2018}
      {Bachelor of Technology -- Computer Science Engineering}{New Delhi, India}
\resumeSubHeadingListEnd

\section{Certifications}
\resumeSubHeadingList
  \resumeItem{\href{https://verify.skilljar.com/c/ufyhuqnu7z75}{Claude with the Anthropic API} -- Anthropic, 2025}
  \resumeItem{\href{https://verify.skilljar.com/c/5wq8kmpa2jbk}{Claude Code in Action} -- Anthropic, 2025}
  \resumeItem{\href{https://verify.skilljar.com/c/f5vktmpg7und}{Introduction to Agent Skills} -- Anthropic, 2025}
  \resumeItem{\href{https://verify.skilljar.com/c/73xymxvikxt7}{Introduction to Model Context Protocol} -- Anthropic, 2025}
\resumeSubHeadingListEnd

\end{document}
